Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-09 papers/eccv2018/2_method.tex
papers: added comments from Daniel and create outline for supplemental materials

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the segmentation.
There are edges between all nodes that we consider as merge candidates.
Ideally, our graph has edges corresponding to all of the segments that were erroneously split. 
To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). 
The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. 
From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. 
To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities. 
We then use a multicut algorithm to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. 
We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.

@@

The simplest node generation strategy creates one node for every unique segment label in the input volume. 
However, some of the millions of labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels (\TODO{~XX\SI{}{\nano\meter^3}}). 
This removed on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}). Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

@@

A typical approach for generating edges produces one between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. We identify a smaller number of pairs of segments to consider as graph edges using the following approach.

First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching. 
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$.
Elements of $\mathbb{S}_e^\prime$ are candidates for merging. 
However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. 
In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. 
If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.

@@

We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This significantly reduces the need for generating costly manually-labeled ground truth.

@@

After constructing the 3D graph we apply graph partitioning with a multicut formulation to compute the final segmentation. 
Using this global graph partitioning allows us to apply biological constraints on the output. 
The multicut minimization problem allows us to guarantee globally consistent solutions where every cycle is ``closed'' under merging.
To solve this constraining multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
We extend the multicut formulation to the ``lifted'' version of the problem where non-adjacent nodes have ``lifted'' edges.
These edges penalize or reward distance nodes for belonging to the same segment and produce benefits over traditional multicut. 
We determine the lifted edge weights following the example of Beier et al~\cite{beier2017multicut}.
We run the traditional multicut algorithm on our graph varying a bias parameter that encourages over- and under-segmentation. 
\TODO{ADD ADDITIONAL FEATURES}

>>>>

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the segmentation.
There are edges between all nodes that we consider as merge candidates.
Ideally, our graph has edges corresponding to all of the segments that were erroneously split. 
To compute this graph we generate a skeleton for every segment in the pixel-based segmentation (Fig.~\ref{fig:overview}). 
The skeletonized 3D network is a simplified representation of the overall branching structure of the neurons. 
From these skeletons we identify potential merge locations and produce the corresponding edges for the graph. 
To find actual merges we run a classification CNN to generate edge weights corresponding to merge probabilities.
We formulate our graph partitioning problem as a multicut problem to segment the nodes into correct neuronal processes. 
We will now discuss the three major components to our framework (graph creation, edge weight assignment, and graph partitioning) in more detail.

@@

The simplest node generation strategy creates one node for every unique segment label in the input volume. 
However, some of the labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
We prune these nodes from the graph by removing all segments with fewer than a threshold $t_{seg} = 20,000$ voxels (\TODO{~XX\SI{}{\nano\meter^3}}). 
This removed on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}). Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.
\TODO{How much does this change VI - should that matter?}
\TODO{Picture of these examples}

@@

A typical approach for generating edges produces one between all adjacent segments. Two segments $l_1$ and $l_2$ are considered adjacent if there is a pair of adjacent voxels with one labeled $l_1$ and the other labeled $l_2$.
For example, pixel-based agglomeration methods such as NeuroProof~\cite{10.1371/journal.pone.0125825} and GALA~\cite{nunez2014graph} consider all pairs of adjacent segments for merging.
However, this method produces too many edges in the graph for graph-based optimization approaches. 
We identify a smaller number of pairs of segments to consider as graph edges using the following approach.
\TODO{address comment from that one reviewer}

First, we extract a skeleton from each segment in the label volume using a variant~\cite{zhao2014automatic} of the TEASER algorithm~\cite{sato2000teasar}. 
This skeletonization algorithm repeatedly uses Dijkstra's algorithm to find the farthest voxel from a seed location. 
Since this algorithm is non-linear in the number of voxels, we downsample the datasets so that there are voxel samples every $\SI{30}{\nano\meter}$ in each dimension.
Empirically, this reduced the running time for skeletonization by $\TODO{XX\%}$, with minimal reduction in skeleton accuracy ($\TODO{XX\%}$ fewer branches). 
Fig.~\ref{fig:skeletonization} shows three examples of extracted skeletons (in black). 
These skeletons consist of a sequence of \textit{joints}, i.e., locations that are locally a maximum distance from the segment boundary, with line segments connecting successive joints. 
We prune the joints that are within $t_{jnt} = \TODO{XX}\SI{}{\nano\meter}$ of each other to reduce unnecessary branching. 
\TODO{why this value?}
We refer to joints that have only one connected neighbor as \textit{endpoints}. 
Many of the segments that are erroneously split have nearby endpoints  (Fig.~\ref{fig:merge_candidates}). 
\TODO{Numbers for this?}
We make use of this fact to find merge candidates with the following two-pass pruning algorithm.

In the first pass, we iterate over all endpoints $e$ belonging to a segment $S$ and create a set of segments $\mathbb{S}_e^\prime$ that includes all labels that are within $t_{low}$ voxels from $e$.
Elements of $\mathbb{S}_e^\prime$ are candidates for merging. 
However, this first pass often leads to too many candidates, requiring an additional pass for further pruning. 
In the second pass, we consider all of the segments in $\mathbb{S}_e^\prime$ for every endpoint $e$. 
If a segment $S^\prime \in \mathbb{S}_e^\prime$ has an endpoint within $t_{high}$ voxels of $e$, the segment $S$ and $S^\prime$ are considered for merging. 
We store the midpoints between the two endpoints as the center of the potential merge in the set $\mathbb{S}_c$. 
This algorithm produces a set of segments to consider for merging. Only these pairs have a corresponding edge in the constructed graph.
\TODO{From Daniel: this sounds like a double threshold to me.. imho 1-2 sentences without formulas is clearer?}

@@

We extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

@@

After constructing the 3D graph we seek to partition the graph into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input graph itself. 
Second, this minimization produces globally consistent solutions (i.e. a boundary remains if and only if the two corresponding nodes belong to unique segments).

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized ``lifted'' multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the ``lifted'' extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called ``lifted'' edges. 
Ideally these ``lifted'' weights represent the probability that two nodes belong to the same neuron given all such possible paths in the graph between the nodes.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
Since our graphs are sufficiently small, we can generate ``lifted'' edges between all pairs of nodes.

### 2018-03-09 papers/eccv2018/3_evaluation.tex
papers: added comments from Daniel and create outline for supplemental materials

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from two different species.

@@

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$.

@@

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
At the same time this framework produces lower over-segmentation than standard algorithms. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segments pairs. 
After considering various thresholds, we find that $t_{low} = \SI{240}{\nano\meter}$ and $t_{high} = \SI{400}{\nano\meter}$ produce reasonable results on our training data considering this objective.

In our implementation we use nanometers for these thresholds and not voxels. 
Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime. 
For example, the thresholds in voxels are $t_{low} = (40, 40, 8)$ and $t_{high} = (100, 100, 20)$ for the anisotropic Kasthuri dataset and $t_{low} = (24, 24, 24)$ and $t_{high} = (60, 60, 60)$ for the isotropic FlyEM dataset.

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

>>>>

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.

@@

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male \textit{Drosophila} fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}.
The mushroom body in this species is the primary site of associative learning. 
The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume with a resolution of $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ per voxel. 
We use two cubes (Vol. 1 and Vol. 2) of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$ or $999 \times 999 \times 999$ voxels.

@@

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we applied a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.

@@

The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.

In our implementation we use nanometers for these thresholds and not voxels. 
Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
Although the voxels vary between different datasets, the physical space remains constant.

@@

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive merge examples and \TODO{7000} negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-03-09 papers/eccv2018/4_results.tex
papers: added comments from Daniel and create outline for supplemental materials

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as out input dataset with an agglomeration threshold of 0.3 for all datasets. 
The results from our method are shown in red for varying the $\beta$ parameter. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \TODO{XX}\% on the three testing datasets. 
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%). 
This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.

Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. 
Several of these examples combine multiple consecutive segments that span the volume.
In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
Fig.~\ref{fig:qualitative-results} shows typical failure cases of our method (red circles).
In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

@@

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
We present additional analysis of the skeletonization parameters in the supplemental material.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
This is a large benefit over enforcing segment adjacency.

@@

Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
%We train our CNN using one of the Kasthuri volumes and test using the other three datasets.
Since our CNN only takes as input a region of the label volume we can train on  anisotropic data and test on isotropic data.
This provides a major benefit given the time-intensive task of manually generating ground truth for each dataset at various resolutions.

As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
To test this hypothesis, we also evaluate the performance of the FlyEM datasets when the network trains on FlyEM Vol. 1 and infers on FlyEM Vol. 2.\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.}
The blue dotted curve in the figure shows a slight performance increase in this case. However, the improvement is minor, which led us to use the CNN trained on the anisotropic data for the rest of our experiments.

@@

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.
Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.

>>>>

In Fig.~\ref{fig:variation-of-information}, we show the VI results of the pixel-based reconstructions of the Kasthuri and FlyEM data (Sec.~\ref{sec:neuroproof}) for varying thresholds of agglomeration (green). 
We use one of these segmentations (green circle) as our input dataset with an agglomeration threshold of 0.3 for all datasets. 
The results from our method are shown in red for varying the $\beta$ parameter. 
We show comparisons to an oracle (blue) that correctly partitions the graph from our method based on ground truth.

Our algorithm improves the accuracy of the reconstruction for every dataset, reducing the VI split score on average by \TODO{XX}\% on the three testing datasets. 
Scores closer to the origin are better for this metric, and in every instance our results are below the green curve.
We see significant improvements on the Kasthuri datasets (VI split reduction of \TODO{XX}\% and \TODO{XX}\% on the training and testing datasets respectively) and more modest improvements on the FlyEM datasets (reduction of \TODO{XX}\% and \TODO{XX}\%). 
\TODO{FIX: This is because the baseline segmentation algorithm for the isotropic FlyEM data (Sec.~\ref{sec:neuroproof}) performs much better, reducing the potential for improvements. 
Isotropic datasets are easier to segment using state-of-the-art region-based methods than anisotropic ones~\cite{plaza2014annotating}.}

Fig.~\ref{fig:qualitative-results} (left) shows successful merges on the Kasthuri Vol. 2 dataset. 
Several of these examples combine multiple consecutive segments that span the volume.
In the third example on the left we correct the over-segmentation of a dendrite and attached spine-necks.
Fig.~\ref{fig:qualitative-results} (right) shows typical failure cases of our method (red circles).
In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

@@

Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., \TODO{XXX} compared to \TODO{XXX}). 
Our pruning heuristic removes at least $\TODO{X}\times$ the number of edges on all datasets, achieving a maximum removal rate of $\TODO{XX}\times$.
However, there are some adjacent over-segmented labels which are considered. 
Table~\ref{table:skeletonization} shows the results for our edge generation including the number of missed neighbors and potential penalty in VI score.
\TODO{augment table}
We present additional analysis of the skeletonization parameters in the supplemental material.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
On average in our datasets we correctly merge \TODO{XX} number of non-adjacent segments.

@@

Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
\TODO{As shown by the ROC curve, the test results on the Kasthuri data are better than the results for FlyEM.
We believe this is in part because of the differences in the datasets (i.e., isotropy and $xy$ resolution).
To test this hypothesis, we also evaluate the performance of the FlyEM datasets when the network trains on FlyEM Vol. 1 and infers on FlyEM Vol. 2.\footnote{Since the FlyEM datasets have significantly fewer examples, we initialize the network with the weights from the Kasthuri training and have an initial learning rate of $10^{-4}$.}
The blue dotted curve in the figure shows a slight performance increase in this case. However, the improvement is minor, which led us to use the CNN trained on the anisotropic data for the rest of our experiments. -- FIX THIS, also AUC values}

@@

\paragraph{Neural Network Transference.}

Our neural network does not take as input the images or affinities to allow us to transfer network weights from one dataset to the next.
Table~TODO{X} shows the result when training on the FlyEM data and inferring on the Kasthuri data and vice versa.
The classification results are reasonable despite the fact that the datasets vary in resolution and even animal type.

@@

The graph optimization strategy using multicut increases our accuracy over using just the CNN.
Table \ref{table:multicut} shows the changes in precision, recall, and accuracy for all four datasets compared to the CNN.
The precision increases on each dataset, although the recall decreases on all but one of the datasets.Since it is more difficult to correct merge errors than split errors, it is often desirable to sacrifice recall for precision.
Over the three testing datasets, applying a graph-based partitioning strategy reduced the number of merge errors by \TODO{XX}\%, \TODO{XX}\% and \TODO{XX}\%, respectively.
